---
title: "Takeda EDA"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(chron)
library(viridis)
```

# EDA OVERVIEW

## Questions of Interest

- How has per student consumption changed over time? 
- Every year a new freshman class comes in - how has the consumption for incoming freshman classes changed? I think this can provide valuable insights for how desnat and other courses influence students. Similarly, can we break out each class year into their own 4 year "story" to see how they 3d printed more or less over time? 
- Similarly, if you break down each years into freshman-senior earmarked consumption, which classes print the most each year? is it consistent (i.e. sophomores always win). 
- Lastly, looking into how the class related consumptions have changed over the time they have been recorded
- Also, last but probably most important - if there is any data that you think other schools could provide that would be interesting to compare Olin's metrics to, i.e. how much filament they buy or # of students with access, Daniela has contacts I need to reach out to with some Q's


## Hypotheses to Explore

- Does first year desnat usage correlate with print usage following? 
- How does print habits change over time within a given class? 
- Percentage of total printing associated with a given class

## Questions from Data Analysis

- Source of population on campus numbers? 
  - Is there a directory of students? 
- How many students actually fill out the print log? How representative is this data? 
  - Send student survey asking for estimates for how often students fill out the survey? 
- 

## Improvements to Data

- Ask students to use student ID number instead of name? Or use dropdown as current system is awful for data sorting
- 


```{r load data frames}
getwd()
load("data/df_both.Rdata")
load("data/df_graph.Rdata")
load("data/df_both_names.Rdata")
```

```{r}
df_both %>% 
  glimpse()

df_graph %>% 
  glimpse()

df_both_names %>% 
  glimpse()
```

```{r}
df_just_names <- df_both_names %>% 
  select(name) %>% 
  distinct(name)

write.csv(df_just_names, file = "data/df_just_names.csv")
```



```{r}
df_both %>% 
  count(reason_print) %>% 
  filter(!is.na(reason_print)) %>%
  mutate(
    reason_print = reorder(reason_print, -n)
  ) %>%
  ggplot(aes(x = reason_print, y = n, fill = reason_print)) +
  geom_col(show.legend = FALSE) +
  theme_common() +
  # theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(axis.text.x = element_text(size = 9)) +
  labs(
    title = "Print Reasons \n",
    x = "Reason",
    y = "Count"
  ) +
  geom_text(aes(label = n), size = 3.5, vjust = -.2, colour = "black") 
#ggsave("figures/printReasonsWithLabels.jpg", dpi = 500, bg = "white")

df_both %>% 
  group_by(reason_print) %>% 
  #filter(!is.na(reason_print)) %>%
  summarize(
    print_mass = sum(print_mass, na.rm = TRUE)
  ) %>% 
  ggplot(aes(x = reason_print, y = print_mass, fill = reason_print)) +
  geom_col(show.legend = FALSE) +
  theme_common() +
  # theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(axis.text.x = element_text(size = 9)) +
  labs(
    title = "Print Mass \n",
    x = "Print Reason",
    y = "Mass (g)"
  ) +
  geom_text(aes(label = print_mass), size = 3.5, vjust = -.2, colour = "black") 
#ggsave("figures/printReasonsMassWithLabels.jpg", dpi = 500, bg = "white")

```

## Observations 
- Unclear why NA is so high compared to all other sources
- Is this due to high volume users or due to individuals not reporting the print reason

